Dataset-level report

### 2019-11-08 analysis/reports/dat_report_template.Rmd
fix hist issue

```{r plot nb samples}
samples_hist <- ggplot(data = site_samples, aes(x = nsamples)) +
  geom_histogram(binwidth = 10) +
  theme_bw() +
  facet_wrap(vars(singletons), nrow = 1) +
  ggtitle("Number of samples achieved") +
  xlim = c(-11, max(site_samples$nsamples) + 11)

>>>>

```{r plot nb samples}
samples_hist <- ggplot(data = site_samples, aes(x = nsamples)) +
  geom_histogram(binwidth = 10) +
  theme_bw() +
  facet_wrap(vars(singletons), nrow = 1) +
  ggtitle("Number of samples achieved")  +
  xlim(c(-11, max(site_samples$nsamples) + 11))
